A molecular dynamics study of the solvation of CO\textsubscript{2}, water, and some organic compounds in the ionic liquids [emim][B(CN)\textsubscript{4}] and [emim][NTf\textsubscript{2}]

### 2018-02-19 ionic_liquids.tex
begin discussion section

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{scalerel}
\usepackage{natbib}

\usepackage{adjustbox}   
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{colortbl} 
\usepackage{xcolor}
\usepackage{float}
\usepackage{flafter}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{graphicx,bm}
\usepackage[]{subfig}
\usepackage{epstopdf}

\biboptions{sort&compress}
\modulolinenumbers[5]

@@

For the determining the initial configuration to specify for the rigid bodies we performed a preliminary study of the dihedrals in the ethyl group of [emim]$^{+}$, as we consider that its flexibility  may introduce a more significant conformational change in the cation. Small anions are usually simulated as rigid bodies. The nomenclature of the atoms are shown in Fig.~\ref{fig:atoms_name}. In the \textit{united-atoms} version of [emim]$^{+}$,  the nomenclature is identical, but hydrogens ranging from H4 to H11 are eliminated.

@@

A first inspection of Fig.~\ref{fig:dihedrals}, reveals a similar behavior of the models of Refs.~\cite{Koller_2012} and Liu.~\cite{Liu_2014}. This was previsible

\begin{figure}
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
\label{fig:atoms_name}
\end{figure}

%\begin{figure*}
%\centering
%\subfloat[text for the first subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{koller}%
%}
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{batista}%
%}
%
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{Liu}%
%}
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{Weber}%
%}
%\caption{ggggg}
%\label{fig:dihedrals}
%\end{figure*}

%\begin{figure}
%\centering
%\subfloat[text for the first subfigure\label{sfig:testa}]{%
%  \includegraphics[width=\linewidth]{Ludwig}%
%}
%
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=\linewidth]{Ludwig_anion}%
%}
%\caption{}
%\label{}
%\end{figure}

\begin{table*}[htp]
\caption{Densidades de [emim][B(CN)\textsubscript{4}] calculadas a partir simulaciones de NPT DM 298.15 K y 1 atm. La densidad experimental corresponde a $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{threeparttable}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
$\text{[emim]}$[B(CN)\textsubscript{4}] & $T_{\text{sim}}$ & $ P_{\text{sim}} $ & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (K) &  (atm) &  (g/cm$^{3}$) &  \\
			\hline
		 \multicolumn{5}{c}{Flexible ions/Ewald method}\\

@@

\begin{table*}[htp]
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Resultados de la energía libre de solvatación y de la constante de Henry de CO\textsubscript{2} en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] a T = 298.15 K y P = 1 atm. Los valores experimentales de la constante de Henry en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] corresponden a 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} y a 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectivamente.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Modelo & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{[emim][B(CN)\textsubscript{4}]} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller y col.~\cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista y col.~\cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu y col.~\cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner~\cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann y col.~\cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{figure}
\centering
\subfloat[text for the first subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}
\caption{}
\label{}
\end{figure}

@@

\begin{table*}[htp]
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Resultados de la energía libre de solvatación a T = 298.15 K de las sustancias puras benceno, hexano, ciclohexano, etanol y agua.}
\begin{tabular}{ c c c c c c c c }
\toprule
Soluto & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
 & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
\hline
benceno OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
hexano OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
ciclohexano & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
etanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
agua TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
 \bottomrule
\label{table:mu_solutos} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{table*}[htp]
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Coeficientes de actividad a dilución infinita en [emim][B(CN)\textsubscript{4}] a T = 298.15 K de los solutos benceno, hexano, ciclohexano, etanol y agua.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Soluto & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexano OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
ciclohexano& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benceno OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
agua TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}

>>>>

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage[hidelinks,colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{scalerel}
\usepackage{natbib}

\usepackage{adjustbox}   
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{colortbl} 
\usepackage{xcolor}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{graphicx,bm}
\usepackage[]{subfig}
\usepackage{epstopdf}
\usepackage{float}
\biboptions{sort&compress}
\modulolinenumbers[5]

@@

For the determining the initial configuration to specify for the rigid bodies we performed a preliminary study of the dihedrals in the ethyl group of [emim]$^{+}$, as we consider that its flexibility  may introduce a more significant conformational change in the cation. Small anions are usually simulated as rigid bodies. The nomenclature of the atoms are shown in Fig. In the \textit{united-atoms} version of [emim]$^{+}$,  the nomenclature is identical, but hydrogens ranging from H4 to H11 are eliminated.

@@

A first inspection of Fig.~\ref{fig:atoms_id} reveals a similar behavior of the models developed by Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}. This was expected as in both cases are based on AMBER. In addition, Figs are symmetric, which means that atoms C1-N2-C2 are coplanar.

In the case of , the most likely angles of 90 and 270

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
\label{fig:atoms_id}
\end{figure}

\begin{figure*}
\centering
  \includegraphics[width=.4\linewidth]{koller.png}%
  \includegraphics[width=.4\linewidth]{batista.png}%

  \includegraphics[width=.4\linewidth]{Liu.png}%
  \includegraphics[width=.4\linewidth]{Weber.png}%
\caption{}
\label{k}
\end{figure*}

\begin{figure}[H]
\centering
  \includegraphics[width=\linewidth]{Ludwig.png}%

  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
\caption{lala}
\label{e}
\end{figure}

\begin{table*}
\caption{Densidades de [emim][B(CN)\textsubscript{4}] calculadas a partir simulaciones de NPT DM 298.15 K y 1 atm. La densidad experimental corresponde a $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{threeparttable}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
$\text{[emim]}$[B(CN)\textsubscript{4}] & $T_{\text{sim}}$ & $ P_{\text{sim}} $ & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (K) &  (atm) &  (g/cm$^{3}$) &  \\
			\hline
		 \multicolumn{5}{c}{Flexible ions/Ewald method}\\

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Resultados de la energía libre de solvatación y de la constante de Henry de CO\textsubscript{2} en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] a T = 298.15 K y P = 1 atm. Los valores experimentales de la constante de Henry en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] corresponden a 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} y a 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectivamente.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Modelo & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{[emim][B(CN)\textsubscript{4}]} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller y col.~\cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista y col.~\cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu y col.~\cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner~\cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann y col.~\cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{figure}
\centering
\subfloat[text for the first subfigure]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

\subfloat[text for the second subfigure]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}
\caption{}
\label{f}
\end{figure}

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Resultados de la energía libre de solvatación a T = 298.15 K de las sustancias puras benceno, hexano, ciclohexano, etanol y agua.}
\begin{tabular}{ c c c c c c c c }
\toprule
Soluto & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
 & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
\hline
benceno OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
hexano OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
ciclohexano & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
etanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
agua TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
 \bottomrule
\label{table:mu_solutos} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Coeficientes de actividad a dilución infinita en [emim][B(CN)\textsubscript{4}] a T = 298.15 K de los solutos benceno, hexano, ciclohexano, etanol y agua.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Soluto & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexano OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
ciclohexano& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benceno OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
agua TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}
